Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-11 documentation/paper.tex
Cleared up wording for supervised learning introduction

These conversion, preprocessing, and data cutting steps were reapplied during this study, and are described in section \ref{data_formats}.

@@

2 semi-supervised algorithms were developed and implemented for this study: gravitational differentiation and iterative cluster nucleation. Both are discussed in detail in section \ref{semi_supervised}.

@@

Important unknowns to be determined through experimentation with supervised learning included the most effective input format for the network, and the associated general network structure. Three major such configurations were applied:

>>>>

These conversion, preprocessing, and data cutting steps were reapplied during this study, and are described in Section \ref{data_formats}.

@@

2 semi-supervised algorithms were developed and implemented for this study: gravitational differentiation and iterative cluster nucleation. Both are discussed in detail in Section \ref{semi_supervised}.

@@

Supervised learning is the most common machine learning paradigm, in which a system is trained on a training set of predefined inputs and ground truths.

As overviewed in Section \ref{data_formats}, there are many possible formats for the input. In addition, different network architectures are necessitated to process these inputs. Three major such configurations were tested:
